Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

We argue that the $k$-tuple $(r_1, ..., r_{k-2}, h, v)$ belongs to $\J(R_1,...,$ $R_{k-2},H,V)$. Clearly, $r_z$ covers $\bm{t}[z]$ for all $z \in [k-2]$. Thus, $\bigcap_{z=1}^{k-2} r_z$ covers $\bigcap_{z=1}^{k-2} \bm{t}[z]$, which is $B_\bm{t}$. Hence, point $p$ --- which is the intersection point of $h$ and $v$ and a corner of $B_\bm{t}$ --- falls in $\bigcap_{z=1}^{k-2} r_z$, indicating $h \cap v \cap \bigcap_{z=1}^{k-2} r_z \ne \emptyset$. We map $\bm{t}$ to $(r_1, ..., r_{k-2}, h, v)$.

@@

s

>>>>

We argue that the $k$-tuple $(r_1, ..., r_{k-2}, h, v)$ belongs to $\J(R_1,...,$ $R_{k-2},H,V)$. Clearly, $r_z$ covers $\bm{t}[z]$ for all $z \in [k-2]$. Thus, $\bigcap_{z=1}^{k-2} r_z$ covers $\bigcap_{z=1}^{k-2} \bm{t}[z]$, which is $B_\bm{t}$. Hence, point $p$ --- which is the intersection point of $h$ and $v$, and also a corner of $B_\bm{t}$ --- falls in $\bigcap_{z=1}^{k-2} r_z$, indicating $h \cap v \cap \bigcap_{z=1}^{k-2} r_z \ne \emptyset$. We map $\bm{t}$ to $(r_1, ..., r_{k-2}, h, v)$.

@@

It remains to prove that no two distinct tuples $\bm{t}_1, \bm{t}_2 \in \J(R_1',...,R_{k-2}')$ can be mapped to the same tuple in $\J(R_1,..., R_{k-2},$ $H, V)$. Assume that this is not true, namely, both $\bm{t}_1$ and $\bm{t}_2$ are mapped to $(r_1, ..., r_{k-2}, h, v) \in \J(R_1,..., R_{k-2}, H, V)$. However, in this case, $\bm{t}_1[z]$ is the trimmed rectangle of $r_z$ for all $z \in [k-2]$, and $\bm{t}_2[z]$ is the trimmed rectangle of $r_z$ for all $z \in [k-2]$. This indicates $\bm{t}_1 = \bm{t}_2$, giving a contradiction.
